Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-23 edubots_surveys.Rnw
reorganizes text for RQ1 and script for sample population description refs #13

According to the results summarized in Fig. \ref{figure:chatbots_use_gender_age_exp}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain. Finally, about 20\% also use Telegram. 
Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more). Also, teachers in vocational Education also use Whatsapp more than university teachers.

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
    \end{minipage}
\end{center}
    \caption{Use of chatbots in class: distributions per gender and age. Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
\label{figure:chatbots_use_gender_age_exp}
\end{figure}

Results in Fig. \ref{figure:chatbots_use_sector_discip} do not show differences in the use of instant messaging apps between teachers from University and vocational education. In general, most teachers prefer messaging apps provided by their own institutions. With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
    \end{minipage}

    \vspace{2mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
    \end{minipage}
\end{center}
    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
\label{figure:chatbots_use_sector_discip}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
\caption{XXX}
\label{figure:chatbots_messagingorganization}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.47\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
    \end{minipage}
\end{center}
    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
\label{figure:chatbots_use_postcovid}
\end{figure}

>>>>

According to the results summarized in Fig. \ref{figure:chatbots_use}, teachers mainly use the instant messaging app provided by their institutions (55\%),  and Whatsapp (44\%), the most popular messaging app in Spain. Finally, about 20\% also use Telegram. 
Although gender differences are not significant, female teachers answered they use instant messaging apps more than male teachers (about 10\% more). Also, teachers in vocational Education also use Whatsapp more than university teachers.

@@

\begin{figure}[!ht]
\begin{center}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_provided.pdf}
    \end{minipage}
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_provided.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_provided.pdf}
    \end{minipage}
    %----
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_whatsapp.pdf}
    \end{minipage}
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
    \end{minipage}
    %----
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/age_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_telegram.pdf}
    \end{minipage}
    %----
    \vspace{0.5mm}
    \begin{minipage}[t]{0.30\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.50\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
    \end{minipage}
\end{center}
    \caption{Use of chatbots in class: distributions per gender, age, years of experience in education, university or vocational education, and discipline. Teachers were specifically asked about two popular instant messaging apps (Whatsapp and Telegram), and the use of platforms already provided by their institutions different than these two ones.}
\label{figure:chatbots_use}
\end{figure}

Results in Fig. \ref{figure:chatbots_use} do not show differences in the use of instant messaging apps between teachers from University and vocational education. In general, most teachers prefer messaging apps provided by their own institutions. With respect to specific disciplines, Engineering and Technology teachers are more active in their use, although it is also relevant the amount of teachers from Humanities that answered they used these apps in their classes (around 60\% use the apps provided by their institutions).

%\begin{figure}[t]
%\begin{center}
%    \vspace{2mm}
%    \begin{minipage}[t]{0.30\textwidth}
%	    \centering
% 	    \includegraphics[width=\textwidth]{figures/sector_whatsapp.pdf}
%    \end{minipage}
%    \begin{minipage}[t]{0.50\textwidth}
%	    \centering
% 	    \includegraphics[width=\textwidth]{figures/discipline_whatsapp.pdf}
%    \end{minipage}
%    
%    \vspace{2mm}
%    \begin{minipage}[t]{0.30\textwidth}
%	    \centering
% 	    \includegraphics[width=\textwidth]{figures/sector_telegram.pdf}
%    \end{minipage}
%    \begin{minipage}[t]{0.50\textwidth}
%	    \centering
% 	    \includegraphics[width=\textwidth]{figures/discipline_telegram.pdf}
%    \end{minipage}
%\end{center}
%    \caption{Differences in the use of chatbots in class between vocational and university teaching and distributions by discipline.}
%\label{figure:chatbots_use_sector_discip}
%\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=\textwidth]{figures/messaging_organization.pdf}
\caption{Distribution of teachers' preferences for the chat groups with their students: from groups only with their students from a specific course to groups with greater social interaction with all students in their School or Faculty.}
\label{figure:chatbots_messagingorganization}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
    \begin{minipage}[t]{0.75\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/gender_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.75\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/sector_covid.pdf}
    \end{minipage}
    \begin{minipage}[t]{0.75\textwidth}
	    \centering
 	    \includegraphics[width=\textwidth]{figures/experience_covid.pdf}
    \end{minipage}
\end{center}
    \caption{Impact of COVID in the use of messaging apps in University and vocational education.}
\label{figure:chatbots_use_postcovid}
\end{figure}
